Adopting agile in the large: motivations, success factors and challenges

### 2013-11-07 journal/article.tex
Filtering; note on include/exclude
Notes on include criteria

>>>>

--> Case of one agile team in an enterprise: This is unrelated if the single
    team has no effect on the rest of the enterprise. There is no
    ``organizational transformation'' if there is just one team soloing.

--> Transformation and ``scaling up'' are very closely related. In some cases
    they can not really be separated. For instance, if transformation begins
    with a pilot and spreads gradually through the organization, it is very
    likely that the process is seen as a ``scaling up'' journey.
    However, in general, we do not include discussions purely on scaling up,
    especially if no organizational change is considered.
